logistic regression

### 2021-07-13 scripts/62_logistic_regression_version.Rmd
update

# the CLR transformed genera abundance 
clr <- read_csv('../data/amplicon/stool/counts_genus_combined_CLR.csv')  %>% 
  spread(key = 'genus', value = 'clr')

@@

```{r}
g_tox <- glm(
  toxicity ~ Akkermansia + Bacteroides + Enterococcus + Faecalibacterium + Ruminococcus + center, 
  data = gmeta, 
  family = binomial(link = "logit")
)
summary(g_tox)

gb <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides')) %>% plot()
gr <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus')) %>% plot()
ge <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus')) %>% plot()
ga <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia')) %>% plot()
gf <- ggpredict(g_tox,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium')) %>% plot()

plot_model(g_tox)+
  ggsave('../figs/amplicon/genera_tox_logi_CLR.pdf', height = 3, width = 4)
```

```{r}
gtox_clr <- ggarrange(gb, gr, ge, ga, gf,
    ncol = 1
    #o = 'hv',
    #labels = 'AUTO',
    #axis = 'bltr'
    )  
```

@@

```{r}
g_CR <- glm(
  cr_d100 ~ Akkermansia + Bacteroides + Enterococcus + Faecalibacterium + Ruminococcus + center, 
  data = gmeta, 
  family = binomial(link = "logit")
)
summary(g_CR)

gb <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Bacteroides')) %>% plot()
gr <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Ruminococcus')) %>% plot()
ge <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Enterococcus')) %>% plot()
ga <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Akkermansia')) %>% plot()
gf <- ggpredict(g_CR,se=TRUE,interactive=TRUE,digits=3, c('Faecalibacterium')) %>% plot()

plot_model(g_CR)+
  ggsave('../figs/amplicon/genera_cr_logi_CLR.pdf', height = 3, width = 4)
```

```{r}
gCR_clr <- ggarrange(gb, gr, ge, ga, gf,
    ncol = 1
    #o = 'hv',
    #labels = 'AUTO',
    #axis = 'bltr'
    ) +
    ggsave(str_glue('../figs/amplicon/gcr_CLR_5.pdf'), width = 3, height = 8, dpi = 300)
```

@@

plot_model(g_tox) +
  ggsave('../figs/amplicon/genera_tox_logi_log10.pdf', height = 3, width = 4)
```

@@

>>>>

@@

@@

@@

# plot_model(g_tox) +
#   ggsave('../figs/amplicon/genera_tox_logi_log10.pdf', height = 3, width = 4)
```

```{r}
or_CI <- round(cbind(coef(g_tox), confint(g_tox)), digits=3) %>% 
  as.data.frame()
or_CI <- or_CI %>% 
  mutate(variable=rownames(or_CI)) %>% 
  rename(lower_bound = `2.5 %` , upper_bound = `97.5 %`) 
# Now plot them
or_CI[-c(1,7),] %>%  #remove row number 1 (The intercept)
  ggplot(aes(x = variable, y = V1)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-1.5, 1.5)) +
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'Toxicity') +
  ggsave('../figs/amplicon/logis_genera_tox.pdf', width = 5, height = 4)
```

@@

```{r}
or_CI <- round(cbind(coef(g_CR), confint(g_CR)), digits=3) %>% 
  as.data.frame()
or_CI <- or_CI %>% 
  mutate(variable=rownames(or_CI)) %>% 
  rename(lower_bound = `2.5 %` , upper_bound = `97.5 %`) 
# Now plot them
or_CI[-c(1,7),] %>%  #remove row number 1 (The intercept)
  ggplot(aes(x = variable, y = V1)) +
  geom_point(shape = 15,
             size  = 4, width = 0.1,
             position = "dodge", color="black") +
  geom_errorbar(aes(ymin  = lower_bound,
                    ymax  = upper_bound),
                width = 0.1,
                size  = 0.7,
                position = "dodge", color="turquoise4") +
  theme(axis.title = element_text(face = "bold")) +
  xlab("Variables") + ylab("Coefficient with 95% CI") +
  coord_flip(ylim = c(-1.5, 1.5)) +
  geom_hline(yintercept = 0, color = "red", size = 1) +
   theme(axis.title = element_text(size = 0)) +
  theme(axis.text = element_text(size = 14)) +
  labs(title = 'CR') +
  ggsave('../figs/amplicon/logis_genera_cr.pdf', width = 5, height = 4)
```
